caDDS: Community Assisted Distributed Database for Sequences

### 2020-06-22 Paper2020ACM/Paper2020.tex
Carl updated the project

\subsubsection{Principles of Databases} 
There are 3 principles needed when creating a database. The idea is that only two of the three can be focused on at any given time. Only two since the current technology can only handle two. These principles and limitations need to be taken into consideration when designing the system. \cite{Silberschatz2010}

\begin{itemize}
    \item Consistency - Does the data have integrity? To update one part, all other (replicated) parts should be updated quickly as well; Data is accurate and copied faithfully. An example would be that genes for specimen A, when copied to another data node should contain the exact copy of the data, with no changes.
    \item Accessibility - How easy it is to access data, API protocols? An example would be the number of commands  a user needs to do to access every data.
    \item Partition Tolerance - How resilient is the system when it comes to failures? If one portion breaks, the other portions should still be entirely usable. An example would be a power failure for one system, how would this affect the other systems?
\end{itemize}

@@

>>>>

@@

\subsubsection{CAP theorem for Databases} 
There are 3 principles needed when creating a database. The idea is that only two of the three can be focused on at any given time. Only two since the current technology can only handle two. These principles and limitations need to be taken into consideration when designing the system.

\begin{itemize}
    \item Consistency - Does the data have integrity? To update one part, all other (replicated) parts should be updated quickly as well; Data is accurate and copied faithfully. An example would be that genes for specimen A, when copied to another data node should contain the exact copy of the data, with no changes.
    \item Availability - Is the database usable by clients all of the time? The entire system must be in downtime as infrequently as possible, despite failures.
    \item Partition Tolerance - How resilient is the system when it comes to failures? If one portion breaks, the other portions should still be entirely usable. An example would be a power failure for one system, how would this affect the other systems?
\end{itemize}

Partition tolerance is a de facto requirement of distributed databases and cannot be avoided, so the main trade-off is between availablity and consistency. \cite{Silberschatz2010} Suppose a distributed system prefers consistency. A user updates an SQL row in one partition of the database. Beforehand, this row has already been replicated among many partitions. To ensure that all replicas of the row are consistent, the system must lock this part of the database to prevent other users from reading and editing it, so availability will be affected in the meantime. A distributed system preferring availability, such as a messenger app, will not lock parts of the database in the purpose of being open to serve its users, but cannot guarantee that the data it outputs is always up-to-date. There might be a delay before the data is fully consistent among geographic partitions.
